Quasi-consistent efficient meshfree thin shell formulation to naturally accommodate essential boundary conditions

### 2024-03-10 response.tex

The authors sincerely thank the reviewers for their further comments. Accordingly, the authors have meticulously revised the manuscript and the details are given as follows.

\section*{Reviewer \#1}
\textit{This manuscript provides a meshfree thin shell formulation based on the Hu-Washizu variational principle. The essential boundary conditions in the present formulation do not require additional artificial parameters, which can be considered insensitive to those in Nitsche and Penalty’s approaches. The derivation is rigorous however several issues must be properly addressed before the publication. I recommend a major revision.}

\textbf{1.} \textit{After Eq. 5, the formulation of theta needs to be provided.}

\textbf{Reply:} Thanks. The expression of $\boldsymbol \theta$ is derived by:
\begin{equation}
    \begin{split}
        \epsilon_{3i} = 0 \Rightarrow &
        \left \{
        \begin{split}
            \boldsymbol \theta \cdot \boldsymbol a_\alpha &= - \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3 \\
            \boldsymbol \theta \cdot \boldsymbol a_3 &= 0
        \end{split}
        \right . \\ \Rightarrow &
        \boldsymbol \theta = \underbrace{\boldsymbol \theta \cdot \boldsymbol a_{\alpha}}_{- \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3} \boldsymbol a^\alpha 
        + \underbrace{\boldsymbol \theta \cdot \boldsymbol a_3}_{0} \boldsymbol a^3 = - \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3 \boldsymbol a^\alpha
    \end{split}
\end{equation}
The above derivation is given by Eq. (9). For a better understanding, the expression of Eq. (9) has been improved on Page 6.

@@

\textbf{2.} \textit{Consider using different symbols for the mid-surface displacement, v is always referring to velocity.}

\textbf{Reply:} Thanks to reviewer's suggestion. However, the velocity is not involved in this paper, it will not lead any misunstanding as $\boldsymbol v$ is denoted for deflection. So the $\boldsymbol v$ is still presented the mid-plane deflection.

@@

\textbf{3.} $\boldsymbol \theta$ \textit{is the variation of $\boldsymbol a_3$, so $\boldsymbol \theta \cdot \boldsymbol a_3=0$. This relationship does not come from $\epsilon_{3i} = 0$, which was in Eq. (9).}

\textbf{Reply:} Thanks, the reviewer is right, the rotation $\boldsymbol \theta$ is perpendicular to $\boldsymbol a_3$. However, this relationship is also equivalent with $\epsilon_{3i}=0$, which follows the Kirchhofff hypothesis and can be easily evidenced by expression of Eq. (9).

@@

\textbf{7.} \textit{In Example 5.2, the authors provided the wrong reference value. $-0.3024$ is the one under RM shell theory. In this case, I believe the value should be $-0.3006$. See [1] for more information.}

\textbf{Reply:} Thank you for your suggestion, the reference value has been changed to $-0.3006$. Accordingly, the related statement on Page 21 is modified.

\textbf{8.} \textit{In Example 6.2, also check if the reference value provided in this study is for RM shells [2].}

\textbf{Reply:} Following the reviewer's suggestion, the reference value has been updated in Fig. on Page.

@@

\textbf{9.} \textit{Scodelis-Lo roof, pinched hemisphere, and pinched cylinder are the most famous shell benchmark problems. In [3], the authors named them ”shell obstacle course”. These 3 examples are even harder than those finite deformation shell simulations. So a good shell formulation should be capable of passing these three challenges. It is strongly suggested that the authors add the pinched cylinder simulation to this manuscript.}

\textbf{Reply:} Thank your for reviewer's suggestion. The pinched cylinder is one of the most famous benchmark example for thin shell formulation, and this example is also based on cylinder coordinate system, which is similar with Scodelis-Lo roof problem. So, in this manuscript, the pinched cylinder problem is not considered in this manuscript, and the authors will consider it in further work.

@@

\textbf{1.} \textit{Please check the gramma of the sentence below Eq. (22).}

\textbf{Reply:} Thanks, following the suggestion, this sentence have been revised on Page 9 and the authors have also doubly checked the writing of this revised.

\textbf{2.} \textit{Why is only the quadratic function used for the basis function vector p in Eq. (23)?}

\textbf{Reply:} Thank you for this advised suggestion. The proposed method is in the context of RKGSI framework that can be easily extended for the high order basis functions. However, for conciseness, only quadratic basis function was considered in this study, and the formulation with high order basis functions will be considered in the further work. The related discussion has been added in conclusion on Page 27.

@@

\textbf{3.} \textit{Please provide the meaning of the symbol $s_{\alpha I}$ in Eq. (25). What is the parameter value used in this paper?}

\textbf{Reply:} Thanks for this comment. $s_{\alpha I}$ means the support size of the shape function $\Psi_I$. Following the suggestion, this related statement has been added on Page 9 and the authors have also doubly checked that all the symbols in manuscript have been properly defined.

@@

\textbf{4.} \textit{Fig. 2 contains two sets of integration points. Considering the computational burden, using only one set of integration points may be more beneficial for Galerkin meshfree methods. Therefore, it is recommended to provide some explanations.}

\textbf{Reply:} Thanks for this comment. These two integration scheme contribute different procedures. For instance, in the procedures with blue integration points, there exist both domain integration and boundary integration in each integration cells. The total number of these blue integration points has been optimized from a global point of view to reduce the computation of meshfree shape functions and their first order derivatives. The detailed discussion of these optimized integration scheme can be found in (Wang and Wu, 2019).

On the other hand, the red cross integration points are employed for assembly of stiffness matrix that does not involve any boundary integration, only the integration accuracy is considered for choosing a proper scheme. Thus, the traditional 3-point integration scheme is sufficient for this task. If this integration scheme uses the identical points with blue ones, the number of integration points for assembly have to be two-fold increased, which will lower the efficiency.

Consequently, so far, the integration schemes are the best choice for the proposed method. The related discussion has been added on Page 16.

@@

\textbf{5.} \textit{On page 13, the authors stated that "Even with p-th order variational consistency, the proposed formulation can not exactly reproduce the solution spanned by basis functions". The reproducibility is important for Galerkin meshfree methods. So, just suggestion, is it possible to give some more explicit explanations.}

\textbf{Reply:} Thanks a lot for this helpful comment.

\textbf{6.} \textit{Numerical results of Nitsche's method and penalty method are also shown in Section 5.1. The values of penalty parameters used in the two methods should be provided. In addition, it is encouraged to provide some observations on numerical results of the RKGSI-penalty in Figure 4 and Tables 1 and 2.}

\textbf{Reply:} Following the reviewer's suggestion, the artificial parameters used in NItsche's method and penalty method have been added on Page 19. And the additional demonstrations for RKGSI-penalty also have been added on Pages 19 and 20.

### 2024-03-10 conclusion.tex
20240310

\section{Conclusion}\label{conclusion}
An efficient and quasi-consistent meshfree thin shell formulation was presented to naturally enforce the essential boundary conditions. In this approach, the mixed formulation with Hu-Washizu principle weak form is employed, where the displacement is discretized by traditional meshfree shape functions, the strains and stresses can be expressed by reproducing kernel smoothed gradients and covariant smoothed gradients. The smoothed gradient naturally embed the first two order integration constraint, and has a quasi variational consistency for curved models in each integration cells. Owing to the Hu-Washizu variational principle, the essential boundary condition enforcement has a similar form with conventional Nitsche's method, both have the consistent term and stabilized term. Compared with Nitsche's method, the costly high order derivatives in Nitsche's consistent term have been replaced by smoothed gradients, which shows great computational speed due to the reproducing kernel gradient smoothing framework. Meanwhile, the stabilized term is naturally existed in Hu-Washizu weak form, and the artificial parameter needed in Nitsche's stabilized term has been vanished, which can automatically maintain the coercivity for stiffness matrix. Numerical results demonstrated that the proposed Hu-Washizu quasi-consistent meshfree thin shell formulation show great performance in terms of accuracy, efficiency and stability

>>>>

\section{Conclusion}\label{conclusion}
In this study, an efficient and quasi-consistent meshfree thin shell formulation was presented to naturally enforce the essential boundary conditions.  Mixed formulation with the Hu-Washizu principle weak form is adopted, where the traditional meshfree shape functions discretized the displacement, and the strains and stresses were expressed by the reproducing kernel smoothed gradients and the covariant smoothed gradients, respectively. The smoothed gradient naturally embedded the first second-order integration constraints and has a quasi variational consistency for the curved models in each integration cell. Owing to the Hu-Washizu variational principle, the essential boundary condition enforcement has a similar form with the conventional Nitsche’s method; both have consistent and stabilized terms. The costly high order derivatives in the Nitsche’s consistent term have been replaced by the smoothed gradients, which improved the computational speed due to the reproducing kernel gradient smoothing framework. Furthermore, the stabilized term naturally existed in the Hu-Washizu weak form, and the artificial parameter needed in Nitsche’s stabilized term has vanished, which can automatically maintain the coercivity for the stiffness matrix. Based on general reproducing kernel gradient smoothing framework, the proposed methodology can be trivially extended to high order basis meshfree formulation. The numerical results demonstrated that the proposed Hu-Washizu quasi-consistent meshfree thin shell formulation showed excellent accuracy, efficiency, and stability.
